SMT-Boosted Security Types and Correctness for Low-Level MPC

### 2025-11-24 toplas26/ipj.tex
checkpoint

In all cases, we want to determine the integrity level of computed
values based on assumed partitionings $H,C$. In the previous example,
we want to say that $\rvl{w}$ has low integrity if either client 1 or
2 is corrupt.  To this end we define \emph{security labelings}
$\seclev$ which are mappings from variables $x$ to security levels
$\latel$. By default, given a partitioning $H,C$ this labeling maps
messages to the integrity level of the owner.
\begin{definition}  
  Given $H,C$,
  define $\seclev_{H,C}$ such that $\seclev_{H,C}(\mx{w}{\cid} ) = \hilab$
  if $\cid \in H$  and $\lolab$
  otherwise for all $\mx{w}{\cid}$.
\end{definition}
But the values of messages and reveals may be affected by values sent
by other parties, which is recorded in the $\Delta$ obtained from its
typing. To determine whether this impacts integrity for any given
$H,C$, we apply the inductively defined rewrite relation
$\cheatj{\Delta}{H,C}{\seclev}$, axiomatized in Figure
\ref{fig-cheatj}. The composition of typing and this latter rewriting
obtains essentially a traditional taint analysis, modulo MAC checking.
Our main type soundness result for integrity is then given as follows.
Proof details are given in the Appendix.
\begin{theorem}
  \label{theorem-ipj}
  Given  $\eqspre$ and $\prog$ with
  $\iov(\prog) = S \cup V \cup O$, if
  $\ipj{\eqs}{\prog}{\Delta}$ is valid
  and for all $H,C$ with $\cheatj{\Delta}{H,C}{\seclev}$ 
  we have $\seclev(x) = \hilab$ for all $x \in \houtputs \cup O_H$, then $\prog$
  has integrity for all $H,C$.
\end{theorem}

>>>>

In all cases, we want to determine the integrity level of computed
values based on assumed partitionings $H,C$. In the previous example,
we want to say that $\rvl{w}$ has low integrity if either client 1 or
2 is corrupt.  To this end we define \emph{security labelings}
$\seclev$ which are mappings from variables $x$ to security levels
$\latel$. By default, given a partitioning $H,C$ this labeling maps
messages to the integrity level of the owner.
\begin{definition}  
  Given $H,C$,
  define $\seclev_{H,C}$ such that $\seclev_{H,C}(\mx{w}{\cid} ) = \hilab$
  if $\cid \in H$  and $\lolab$
  otherwise for all $\mx{w}{\cid}$.
\end{definition}
But the values of messages and reveals may be affected by values sent
by other parties, which is recorded in the $\Delta$ obtained from its
typing. To determine whether this impacts integrity for any given
$H,C$, we apply the inductively defined rewrite relation
$\cheatj{\Delta}{H,C}{\seclev}$, axiomatized in Figure
\ref{fig-cheatj}. The composition of typing and this latter rewriting
obtains essentially a traditional taint analysis, modulo MAC checking.
Our main type soundness result for integrity is then given as follows.
Proof details are available in the appendix of \cite{skalka-near-esop25}.
\begin{theorem}
  \label{theorem-ipj}
  Given  $\eqspre$ and $\prog$ with
  $\iov(\prog) = S \cup V \cup O$, if
  $\ipj{\eqs}{\prog}{\Delta}$ is valid
  and for all $H,C$ with $\cheatj{\Delta}{H,C}{\seclev}$ 
  we have $\seclev(x) = \hilab$ for all $x \in \houtputs \cup O_H$, then $\prog$
  has integrity for all $H,C$ and $\adversary$.
\end{theorem}

### 2025-11-24 toplas26/metaty.tex
checkpoint

  \inferrule
      {e_1 \redx \rx{w_1}{\cid_1}\ \cdots\ e_1 \redx \rx{w_n}{\cid_n}}
      {\setit{e_1,\ldots,e_n} \redx
        \setit{\rx{w_1}{\cid_1}, \ldots, \rx{w_n}{\cid_n}}}
  \end{mathpar}
\end{definition}
\noindent We also introduce dependent $\Pi$ types for functions, that allow
dependence on $\stringty$ and $\cidty$ types.
\begin{definition}[$\metaprot$ Function Types]
  Dependent function types are of the syntactic form
  $\Pi y_1,\ldots,y_n. \notg{\Gamma} \rightarrow (\notg{\Gamma}, \notg{R})$.
  where $y_1,\ldots,y_n$ range over $\stringty$ or $\cidty$ types.
\end{definition}
As defined in \TirName{Fn}, a dependent function type $\Pi
y_1,\ldots,y_n. \notg{\Gamma_1} \rightarrow (\notg{\Gamma_2},
\notg{R})$ specifies that, given share typing assumptions in
$\notg{\Gamma_1}$, application the function results in the bindings in
$\notg{\Gamma_2}$ by using the random values in $\notg{R}$. It is
always the case that the type is closed, i.e., only $y_1,\ldots,y_n$
can occur free in $\notg{\Gamma_1}$, $\notg{\Gamma_2}$ $\notg{R}$.
Type checking for functions is accomplished by using fresh ``witness''
values of $\stringty$ and $\cidty$ types to instantiate dependent
variables, similarly to the \TirName{GenEntails} rule. As defined in
the \TirName{App} rule, typing ensures that application of the
function instantiates the dependencies, checks that the instantiation
of $\notg{\Gamma_1}$ is contained in the share typing environment, and
adds the instantiation of $\notg{\Gamma_2}$ as an effect, as will as
the instantiation of $\notg{R}$ with linearity enforced. A practical
programming detail is where the share type environment precondition
$\notg{\Gamma_1}$ is defined.  In our implementation, we write these
as an additional component of \ttt{precondition} annotations, as
illustrated in extended examples discussed in Section
\ref{section-examples}.

@@

Returning to the GMW \ttt{and} gate example introduced in Figure \ref{fig-gmwprepost},
we can extend the definition of \ttt{andgmw} with type annotations to ensure a
valid share typing, as in Figure \ref{fig-gmwsharetypes}. Here a coercion
is needed to specify that the gate output are shares obtained using
$\ttt{r[z]@1}$ as an OTP. The type for $\ttt{andgmw}$ can then be
obtained as:
$$
\ttt{andgmw} : \Pi x,y,z . \varnothing \rightarrow (\setit{[m[z]@1,m[z]@2] : \sharety}, \setit{r[z]@1})  
$$
Note that the function does not require any share type preconditions, since
the (sub)protocol it defines interactively generates new shares using an OTP
($r[z]@1$).

@@

\begin{theorem}
  \label{theorem-metaty}
  Given $\htrip{\eqspre}{\ttt{main()}}{\eqs}$ and $\ttt{main} : \Gamma_1 \rightarrow (\Gamma_2,R)$
  and $\main() \redx \prog$ and $\progpre,\Gamma_1,R' : {OK}$ with $R' \cap R = \varnothing$
  and $\toeq{\progpre} \models \eqspre$. Then $(\progpre;\prog),\Gamma_2,R : {OK}$.
\end{theorem}

Note that Theorem \ref{theorem-metaty} assumes the existence of
$\progpre$ with $\progpre,\Gamma_1,R' : {OK}$ and $R' \cap R =
\varnothing$ and $\toeq{\progpre} \models \eqspre$. The assumption of
some preprocessing protocol such as Beaver triple or MAC share
distribitions is typical, and our approach does not require the
protocol to be defined in detail, just (weakened) postconditions of it
that are sufficient to verify the protocol being programmed.

Theorem \ref{theorem-metaty} also does not provide a complete recipe
for obtaining noninterference modulo output-- as suggested by Theorem
\ref{theorem-sty}, it is also necessary to check closure of
$\Gamma_2$. There are various ways this can be accomplished for the
$\metaprot$ analysis-- for example, we evaluate $\ttt{main}$ to obtain
all program variables and then check closure of $\Gamma_2$ as
prescribed by Definition \ref{def-sty-closed}. We can also add checks
to the type system to guarantee that all messages exchanged between
clients are classified when type checking functions, which is
a simple addition.

>>>>

  \inferrule
      {e_1 \redx \rx{w_1}{\cid_1}\ \cdots\ e_1 \redx \rx{w_n}{\cid_n}}
      {\setit{e_1,\ldots,e_n} \redx
        \setit{\rx{w_1}{\cid_1}, \ldots, \rx{w_n}{\cid_n}}}
  \end{mathpar}
\end{definition}

\noindent We also introduce dependent $\Pi$ types for functions, that allow
dependence on $\stringty$ and $\cidty$ types.
\begin{definition}[$\metaprot$ Function Types]
  Dependent function types are of the syntactic form
  $\Pi y_1,\ldots,y_n. \notg{\Gamma} \rightarrow (\notg{\Gamma}, \notg{R})$.
  where $y_1,\ldots,y_n$ range over $\stringty$ or $\cidty$ types.
\end{definition}
As defined in \TirName{Fn}, a dependent function type $\Pi
y_1,\ldots,y_n. \notg{\Gamma_1} \rightarrow (\notg{\Gamma_2},
\notg{R})$ specifies that, given share typing assumptions in
$\notg{\Gamma_1}$, application of the function results in the bindings
in $\notg{\Gamma_2}$ using the random values in $\notg{R}$ for share
generation or secure openings.  We require that the type is closed,
i.e., only $y_1,\ldots,y_n$ can occur free in $\notg{\Gamma_1}$,
$\notg{\Gamma_2}$ $\notg{R}$.  Type checking for functions is
accomplished by using fresh ``witness'' values of $\stringty$ and
$\cidty$ types to instantiate dependent variables, similarly to the
\TirName{GenEntails} rule. As defined in the \TirName{App} rule,
typing ensures that application of the function instantiates the
dependencies, checks that the instantiation of $\notg{\Gamma_1}$ is
contained in the share typing environment, and adds the instantiation
of $\notg{\Gamma_2}$ as an effect along with instantiation of
$\notg{R}$ with linearity enforced. A practical programming detail is
where the share type environment precondition $\notg{\Gamma_1}$ is
defined by the programmer-- by convention we write these as
additional components of \ttt{precondition} annotations, as
illustrated in the extended examples discussed in Section
\ref{section-examples}.

@@

Returning to the GMW \ttt{and} gate example introduced in Figure \ref{fig-gmwprepost},
we can extend the definition of \ttt{andgmw} with type annotations to ensure a
valid share typing, as in Figure \ref{fig-gmwsharetypes}. Here a coercion
is needed to specify that the gate output wire values are secret-shared using
$\ttt{r[z]@1}$ as an OTP. The type for $\ttt{andgmw}$ can then be
obtained as:
$$
\ttt{andgmw} : \Pi x,y,z . \varnothing \rightarrow (\setit{[m[z]@1,m[z]@2] : \sharety}, \setit{r[z]@1})  
$$
Note that the function does not require any share type preconditions, since
the (sub)protocol it defines interactively generates new shares using an OTP
($r[z]@1$).

@@

\begin{theorem}
  \label{theorem-metaty}
  Given $\htrip{\eqspre}{\ttt{main()}}{\eqs}$ and $\ttt{main} : \Gamma_1 \rightarrow (\Gamma_2,R)$
  and $\main() \redx \prog$ and $\progpre,\Gamma_1,R' : {OK}$ %with $R' \cap R = \varnothing$
  and $\toeq{\progpre} \models \eqspre$. Then $(\progpre;\prog),\Gamma_2,R \uplus R': {OK}$.
\end{theorem}

Note that Theorem \ref{theorem-metaty} assumes the existence of
$\progpre$ with $\progpre,\Gamma_1,R' : {OK}$ and $R' \cap R =
\varnothing$ and $\toeq{\progpre} \models \eqspre$. The assumption of
some preprocessing protocol such as Beaver triple or MAC share
distribitions is typical, and our approach does not require the
protocol to be defined by the programmer, but rather just (weakened)
postconditions of it that are sufficient to verify the protocol being
programmed.

Theorem \ref{theorem-metaty} also does not provide a complete recipe
for obtaining noninterference modulo output-- as per Theorem
\ref{theorem-sty}, it is also necessary to check closure of
$\Gamma_2$. There are various ways this can be accomplished for the
$\metaprot$ analysis-- for example, we evaluate $\ttt{main}$ to obtain
all program variables and then check closure of $\Gamma_2$ as
prescribed by Definition \ref{def-sty-closed}. We can also add checks
to the type system to guarantee that all messages exchanged between
clients are classified when type checking functions, which is
a simple addition.
